\DocumentMetadata{}
\documentclass[11pt,letterpaper]{article}
\usepackage[margin=1in]{geometry}
\usepackage{parskip}

% Fix for TeX Live 2024+ tagging system in tabular environments
\makeatletter
\@ifundefined{tagpdfparaOff}{}{
  \AddToHook{env/tabular*/begin}{\tagpdfparaOff}
  \AddToHook{env/tabular*/end}{\tagpdfparaOn}
  \AddToHook{env/tabular/begin}{\tagpdfparaOff}
  \AddToHook{env/tabular/end}{\tagpdfparaOn}
}
\makeatother

\begin{document}
\pagestyle{empty}

\begin{flushleft}
Jacob Rosario\\
xxx-xxx-xxxx\\
jacobrosario@gmail.com
\end{flushleft}

\vspace{0.5cm}

\today

\vspace{0.5cm}

Hiring Manager\\
LayerZero

\vspace{0.5cm}

Dear Hiring Manager,

I am writing to express my interest in the Backend Engineer position at LayerZero. With my experience in customer service, team collaboration, and a strong understanding of technology, I am confident that I can contribute effectively to your team.

During my time as a Barista at Starbucks and a Sales Associate at Shoe Palace, I honed my customer service skills and learned to work efficiently in fast-paced environments. I handled hundreds of transactions daily, collaborated with diverse teams, and used advanced point-of-sale systems and mobile applications to streamline processes. These experiences have equipped me with the ability to quickly adapt to new technologies and work effectively in dynamic settings.

In addition to my customer service experience, I have a strong technical background. I am proficient in several programming languages, including HTML, CSS, JavaScript, and Python. I am comfortable navigating complex technical stacks and am eager to deepen my expertise in innovative technologies.

I am excited about the opportunity to work at LayerZero and contribute to revolutionizing blockchain interoperability. I am eager to bring my strong problem-solving skills, attention to detail, and passion for technology to your team. I look forward to the possibility of discussing this opportunity further.

Sincerely,

Jacob Rosario

\end{document}