%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% Customized for: Michael Stephenson Chandra
% Elementary Math Tutor Version
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.4 in,top=0.3 in,right=0.4 in,bottom=0.3 in]{geometry}
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}

\name{Michael Stephenson Chandra}
\address{University Student}
\address{+1 (236) 877 5949 \\ michaelschandra1@gmail.com}

\begin{document}

%----------------------------------------------------------------------------------------
% EDUCATION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf Bachelor of Science (Intended Major: Data Science)} \hfill {2024 -- Present}\\
University of British Columbia (UBC)

{\bf IB Diploma} \hfill {Graduated 2024}\\
IPEKA Integrated Christian School, Jakarta, Indonesia \\
GPA: 3.73 \\
Math AA Higher Level: 6

\end{rSection}

%----------------------------------------------------------------------------------------
% SKILLS AND INTERESTS
%----------------------------------------------------------------------------------------

\begin{rSection}{Skills and Interests}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }

Teaching Skills & Elementary mathematics instruction, student engagement, \\
& breaking down concepts, math foundations support, positive guidance \\

Languages & Fluent in English and Bahasa Indonesia \\

\end{tabular}

\end{rSection}

%----------------------------------------------------------------------------------------
% TUTORING EXPERIENCE
%----------------------------------------------------------------------------------------

\begin{rSection}{Tutoring and Classroom Experience}

\begin{rSubsection}{Grade 6 Math Tutor Assistant}{6 months}{Volunteer}{}
\item Tutored students in negative numbers, multiplication, and division.
\item Provided weekly small-group and one-on-one math support.
\item Adapted teaching style to match individual learning needs.
\item Helped students develop confidence in challenging math topics.
\end{rSubsection}

\begin{rSubsection}{Primary Level English Tutor}{6 months}{Volunteer}{}
\item Assisted students with reading comprehension and writing basics.
\item Used structured activities to support early literacy skills.
\item Encouraged participation and built positive learning habits.
\end{rSubsection}

\begin{rSubsection}{Kindergarten Sunday School Assistant}{1 year}{Volunteer}{}
\item Supervised young children during weekly lessons and activities.
\item Supported early learning, communication, and classroom behavior.
\item Helped create an encouraging and safe learning environment.
\end{rSubsection}

\end{rSection}

%----------------------------------------------------------------------------------------

\end{document}
